Topic modeling on EU and the USA research projects

### 2017-06-17 thesis_report/draft_thesis.tex
Topic evolution over time in EU (1/2)

\setlength{\parskip}{1em}
\usepackage[justification=centering]{caption}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{algorithm2e}
\usepackage{url}

@@

>>>>

\setlength{\parskip}{1em}
\usepackage[justification=centering]{caption}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{algorithm2e}
\usepackage{url}
\usepackage{subfig}

@@

One of our goals is to identify trends in scientific research in EU and USA, in
order to give some insights to researchers and scientists regarding potential
trends. Fot this analysis, we run the model for the whole dataset, instead of
running the model per FP), for the EU and the USA, respectively. The outcome was
10 topics for each region from 1994 to 2017 for the EU and from 1994 to 2016 for
the USA.\footnote{in this implementation we removed the projects of the year
2017 from the USA dataset, because the amount of projects-documents was too
small compared to the other years and it was affecting the result of the trend
for eact topic.}

\subparagraph{Trends in the EU}

In figure x we show the 10 topics that consists of the 20 top words with the
highest posterior probability of belonging to the topic. The size of each word
is in proportion to each probability; the bigger the word, the higher the
probability. Each wordcloud describes a topic, which we can find intuitevely.
Below are listed the topics that we found corresponding to the words that
describe them:
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic0_all.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic1_all.png}} &
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic2_all.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic3_all.png}} &
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic4_all.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic5_all.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic6_all.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic7_all.png}} &
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic8_all.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic9_all.png}} &
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\end{figure}
\end{center}

\subparagraph{Trends in the USA	}
